To Do List

### 2018-09-28 ToDo.Rmd
completed tasks

>>>>

## 09/24/18

+ consider inverse normal distribution as another normalization technique
   - understand conceptually what is happening

## 09/24/18

+ disregard count overlaps and use binary overlap with percent overlap if partial
+ reformat table1 into asking question how bad in unbalanced data
 + question 1 should be how severe is unbalanced data?
    - distance not needed here
* consider standardizing data prior to modeling
* is scaling important
 +just percent
 +just dist
 +both unscaled
 +both scaled
